The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
updating coughlin ref

At the heart of all periodic transit search procedures is a filtering step
based on ``box least squares'' \citep[\bls;][]{Kovacs:2002}.
This step produces a list of candidate transit times that is then vetted to
remove the substantial fraction of false signals using some combination of
automated heuristics and expert curation.
In practice, the fraction of false signals can be substantially reduced by
requiring that at least three self-consistent transits be observed
\citep{Petigura:2013, Burke:2014, Rowe:2015, Coughlin:2015}.

@@

Since these data have already been searched for short-period planets, we
assume that all high signal-to-noise candidates with three or more transits
have been previously found \citep{Coughlin:2016}.
To remove these candidates from consideration, we mask the cadences within two
transit durations of the time when a short-period planet candidate is known to
transit.

@@

We start with the PDC-MAP light curves downloaded from
MAST\footnote{\url{https://archive.stsci.edu/kepler/}}.

The \kepler\ Mission measured photometric time series for about 190,000 stars
at half-hour cadence for a baseline of over four years.
We aim to search these light curves for single transits of long-period planets
and single eclipses of binary stars.
These data are made available on
MAST\footnote{\url{https://archive.stsci.edu/kepler/}} and, for each target,
we downloaded the full set of long cadence light curve files provided by Data
Release 24 \citep{Thompson:2015}.
From these files, we extracted the PDC time series and split them into
``sections'' with no more than ten contiguous missing or flagged data points.
The PDC light curves have been corrected for the instrumental effects caused
by the spacecraft using a data-driven model of the focal plane
\citep{Stumpe:2012, Smith:2012}.
Crucially, an attempt is also made by the PDC procedure to remove sharp
instrumental artifacts like ``sudden pixel sensitivity dropouts (SPSDs)''.
The success rate of this correction procedure is much higher than in earlier
data releases but, as discussed in \sect{demo}, there remain some cases that
are not properly accounted for.

The goal of this project is to discover the transits of long-period planets
that have not yet been discovered.
Therefore, when studying the light curve of an eclipsing binary star or a star
with known transiting planet candidates~--~on shorter periods~--~we also remove
all the in-transit data for the candidate using the parameters provided by the
\project{NASA Exoplanet
Archive}\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; We
downloaded the \texttt{cumulative} table of \kepler\ Objects of Interest on
2015-03-25.}.

>>>>

At the heart of all periodic transit search procedures is a filtering step
based on ``box least squares'' \citep[\bls;][]{Kovacs:2002}.
This step produces a list of candidate transit times that is then vetted to
remove the substantial fraction of false signals using some combination of
automated heuristics and expert curation.
In practice, the fraction of false signals can be substantially reduced by
requiring that at least three self-consistent transits be observed
\citep{Petigura:2013, Burke:2014, Rowe:2015, Coughlin:2016}.

@@

Since these data have already been searched for short-period planets, we
assume that all high signal-to-noise candidates with three or more transits
have been previously found \citep{Coughlin:2016}.
To remove these candidates from consideration, we mask the cadences within two
transit durations of the time when a short-period planet candidate is known to
transit\footnote{We specifically use the \textsf{q1\_q17\_dr24\_koi} from the
NASA Exoplanet Archive \url{http://exoplanetarchive.ipac.caltech.edu/}.}.

@@
